\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2018-10-04 document/XSGRB_sample_rev1.tex
Adding some referee response

Using the masked spectrum, the entire process is then repeated 500 times where
the final continuum estimate is the mean of the continuum realizations and the
associated error estimate is the standard deviation. This error reflects the
stability of the algorithm across the spectrum. An example of the performance is
shown in Fig. \ref{fig:spectrum}. In the \lya~forest, where there is very little
flux at the continuum level, the performance of the normalization algorithm
depends on the continuum coverage redwards of the \lya~line. In some cases, very
little continuum is contained in a single arm and a manual continuum estimate is
provided, similar to what is done in \citet{Lopez2016}. In these cases the
continuum error is set to 10 per cent. The code for the continuum estimate is
released along with the paper at
\url{https://github.com/jselsing/XSGRB-sample-paper}.

@@

For the majority of the observation presented in this sample, the slit width of
the target observations is less than the seeing PSF. This means that a fraction
of the incoming light is lost outside the slit. As an example, for atmospheric
conditions delivering a seeing PSF with a FWHM of 0\farc9 observed with a
0\farc9 slit, only 76.1 per cent of the light will enter the slit. This slitloss
is not corrected by the
flux calibration, as flux standard stars are always observed with a 5 \arcsec
slit. As a consequence, almost all spectra will, without slitloss correction,
underestimate the flux by some fraction. Additionally, slitlosses are wavelength
dependent due to the wavelength dependence of seeing \citep{Boyd1978} and as the
seeing changes across the slit in wavelength, so does the slitloss.

To correct for the slitlosses, we develop an algorithm that can, based on the
atmospheric conditions at time of observation and the wavelength dependence of
seeing, estimate the losses at each wavelength bin. We start with the DIMM
seeing \citep{Sarazin1990}, which measures the seeing FWHM at zenith. We correct
the zenith seeing by the airmass of the observational sightline, which gives us
the effective seeing, delivered outside the slit at 5000 \AA. We can then use
that the seeing $\sim \lambda^(1/5)$ to obtain a measure of the seeing across
the entire wavelength coverage of X-shooter. At each wavelength bin of the
spectra, we simulate a synthetic 2D seeing PSF based on a normalised, 2D Moffat
profile which we integrate over the used slit width. The inverse of the fraction
of the light that enters the slit, can then be used to correct for the estimated
slit losses at each wavelength bin.

To assess the accuracy of the flux-calibration, after the slit loss correction,
we compare a subset of afterglow spectra with photometry derived from the
acquisition camera. The acquisition camera takes a short image before
integration and this the delay between the image and the spectroscopic
integration is negligible. We select GRBs at DEC > 30~$^\circ$ to ensure
SDSS coverage, which allows good calibration of the photometric zero point,
acquisition camera magnitude brighter than 21.5 mag, and delay-time between GRB
trigger and spectroscopic observation < 15 hours. These cuts leaves 27
afterglow spectra covering the entire temporal span of the programme. Using this
set we can make a test of the final flux-calibration accuracy.

>>>>

%Using the masked spectrum, the entire process is then repeated 500 times where
%the final continuum estimate is the mean of the continuum realizations and the
%associated error estimate is the standard deviation. This error reflects the
%stability of the algorithm across the spectrum. An example of the performance is
%shown in Fig. \ref{fig:spectrum}. In the \lya~forest, where there is very little
%flux at the continuum level, the performance of the normalization algorithm
%depends on the continuum coverage redwards of the \lya~line. In some cases, very
%little continuum is contained in a single arm and a manual continuum estimate is
%provided, similar to what is done in \citet{Lopez2016}. In these cases the
%continuum error is set to 10 per cent. The code for the continuum estimate is
%released along with the paper at
%\url{https://github.com/jselsing/XSGRB-sample-paper}.

@@

For the majority of the observation presented in this sample, the slit width of
the target observations is less than the seeing PSF. This means that a fraction
of the incoming light is lost outside the slit. As an example, for atmospheric
conditions delivering a seeing PSF with a FWHM of 0\farc9 observed with a
0\farc9 slit, only 76.1 per cent of the light will enter the slit. This slitloss
is not corrected by the flux calibration, as flux standard stars are always
observed with a 5~\arcsec slit. As a consequence, almost all spectra will,
without slitloss correction, underestimate the flux by some fraction.
Additionally, slitlosses are wavelength dependent due to the wavelength
dependence of seeing \citep{Boyd1978} and as the seeing changes across the slit
in wavelength, so does the slitloss. This artificially introduces a change in
continuum slope.

To correct for the slitlosses, we develop an algorithm that can, based on the
atmospheric conditions at time of observation and the wavelength dependence of
seeing, estimate the losses at each wavelength bin. We start with the DIMM
seeing \citep{Sarazin1990}, which measures the seeing FWHM at zenith. We correct
the zenith seeing by the airmass of the observational sightline, which gives us
the effective seeing, delivered outside the slit at 5000 \AA. We can then use
that the seeing scales as $\sim \lambda^{-1/5}$ to obtain a measure of the
seeing across the entire wavelength coverage of X-shooter. At each wavelength
bin of the spectra, we simulate a synthetic 2D seeing PSF based on a normalised,
2D Moffat profile which we integrate over the used slit width. The inverse of
the fraction of the light that enters the slit, can then be used to correct for
the estimated slit losses at each wavelength bin.

To assess the accuracy of the flux-calibration, after the slit loss correction,
we compare a subset of afterglow spectra with photometry derived from the
acquisition camera. The acquisition camera takes a short image before
integration causing the delay between the image and the spectroscopic
integration is negligible. The acquisition camera suffer from varying imaging
quality, lacking calibration files, and regions of reduced thoughput due to
contaminants on the CCD. The derived photometry therefore suffers from
systematics that can be hard to correct for. Because the afterglow brightness
changes rapidly with time, no other imaging are sufficiently close in time to
use.

We select all GRBs for which the aquisition camera used a Sloan filter
\citep{Gunn1998} and is covered by either SDSS \citep{Abolfathi2018} or
Pan-STARRS \citep{Chambers2016}. Additionally we select acquisition camera
magnitude brighter than 21.5 mag, and delay-time between GRB trigger and
spectroscopic observation < 10 hours. These cuts leaves 7 afterglow spectra, for
which a decent calibration of the photometric zero point can be derived. Using
this set we can make a test of the final flux-calibration accuracy.
